Geometrization of characters of tori over non-Archimedean local fields

### 2013-08-14 shanghai.tex
Describe Part 1 in introduction

>>>>

In Part 1 of this paper we study the category $\QC(G)$ of quasicharacter sheaves.
Since it is a rigid symmetric monoidal category,
and the set of isomorphism classes $\QCiso{G}$ forms a group.
Motivated by the sheaf-function dictionary for commutative, connected
algebraic groups \cite{SGA4.5}, we explore the trace of Frobenius morphism
\[
\QCiso{G} \to \Hom(G(\Fq), \EEx)
\]
and show that it is an isomorphism.
